### 2019-02-26 overview.tex
more fiddling with outline

\item highlight persistence

\item highlight composition

\item two dimensions for palette definitions:

  \begin{enumerate}
    \item macros (expressions) vs. functions (values)
    \item analytic (annotated) vs. synthetic (unannotated)
      \begin{itemize}
        \item synthetic requires type splices
        \item an ``untyped'' version that is like synthetic but relies on casts rather than type splices?
      \end{itemize}
  \end{enumerate}

\item live environments (for view function)

  \begin{itemize}
    \item hole for palette application, run, collect hole closures, pass to view
  \end{itemize}

\item two prototype UIs:

  \begin{enumerate}
    \item \Hazel{}: (palette macros;) structure edit actions; expression formula bar; inline layout
    \item \sns{}: (palette functions;) text editor; pop-up menu
  \end{enumerate}

\item (nice-to-have: parameterized palettes; partial application)

\item (nice-to-have: palette definitions in source lang)

>>>>

\item emphasize persistence

\item emphasize composition

\item emphasize liveness

\item mention analytic (annotated) vs. synthetic (unannotated) palettes

  \begin{itemize}
    \item stick to palette macros for now
    \item introduce palette functions in ``Overview Examples: Defining Palettes''
          or ``Formal System''
  \end{itemize}
